---
title: 'R Notebook: Rio package tests'
author: Ben Anderson (b.anderson@soton.ac.uk/@dataknut) [Energy & Climate Change,
  Faculty of Engineering & Environment, University of Southampton]
date: 'Last run at: `r Sys.time()`'
output:
  html_document:
    toc: yes
  html_notebook:
    number_sections: yes
    toc: yes
bibliography: ~/bibliography.bib
---

# Setup
```{r setup}
startTime <- Sys.time() # always good to time your code
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = TRUE)
knitr::opts_chunk$set(message = TRUE)
knitr::opts_chunk$set(fig_caption = TRUE)
knitr::opts_chunk$set(tidy = TRUE)

library(data.table)
library(rio)
library(readr)

dpath <- "~//Data/DECC/NEED/PUF_2014/"
dfile <- paste0(dpath, "need_public_use_file_2014.csv")
dfilegz <- paste0(dpath, "need_public_use_file_2014.csv.gz")
```

Key packages used:

 * base R - for the basics [@baseR]
 * data.table - for fast (big) data handling [@data.table]
 * rio - for import/export [@rio]
 * readr - for .csv reading [@readr]
 * knitr - to create this document [@knitr]
 
# Tests

Now we're going to compare the `fread` function that comes with data.table with the `import` function that comes with rio. We will use a suitably large data file for both:

`r dfile`: `r file.size(dfile)` Mb

First, try `data.table::fread`:
```{r data.tableTest}
system.time(
  freadDT <- fread(dfile)
)
```

Now try `rio::import`:
```{r rioTest}
system.time(
  importDF <- import(dfile) # creates a dataframe
)
```

Now try `readr::read_csv`:
```{r readrTest}
system.time(
  read_csvDF <- read_csv(dfile) # creates a dataframe
)
```

Remember that fread has the *really useful* ability to read from compressed files:

```{r freadGzipTest}
loadcmd <- paste0("gunzip -c ", dfilegz)
system.time(
  freadGzipDT <- fread(loadcmd)
)
```

Which was quicker?

Now convert the data frames created by import and readr to data tables. 

```{r convertDF}
# convert to DT afterwards
system.time(
  importDT <- as.data.table(importDF)
)

system.time(
  read_csvDT <- as.data.table(read_csvDF)
)
```

We would need to allow for this extra time as well so fread from a .gzip looks the best :-)

***
__Meta:__
Analysis completed in: `r round(Sys.time() - startTime,3)` seconds using [knitr](https://cran.r-project.org/package=knitr) in [RStudio](http://www.rstudio.com).

# References

