---
title: 'R Notebook: Stargazer Package Tests'
output:
  html_document:
    toc: yes
  html_notebook:
    number_sections: yes
    toc: yes
---

# Setup
```{r setup}
startTime <- Sys.time() # always good to time your code
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = TRUE)
knitr::opts_chunk$set(message = TRUE)
knitr::opts_chunk$set(fig_caption = TRUE)
knitr::opts_chunk$set(tidy = TRUE)


library(knitr) # for kable
library(stargazer)
```

# Summary

We can print an ordinary table:

```{r oldTable}
summary(cars)
```

# Kable

We can also do that using kable:

```{r kableTable}
t <- summary(cars)
kable(caption = "Cars",
      t
      )
```

# Stargazer

We can also use stargazer:
```{r stargazerTable, results='asis'}
# NB: we need to force knitr to keep the html (asis)
stargazer(cars, type = "html")
```

Although it's not too clear how to change the default cell padding etc.

Stargazer is especially good at regression model outputs:

```{r modelTable, results='asis'}
model1 <- lm(speed ~ dist, cars)
stargazer(model1, type = "html")
```

It has a lot of options that can be used to change what goes where...

***
__Meta:__
Analysis completed in: `r round(Sys.time() - startTime,3)` seconds using [knitr](https://cran.r-project.org/package=knitr) in [RStudio](http://www.rstudio.com).