---
title: "Test Auto-yaml and Tab sets"
author: "Ben Anderson `@dataknut`"
date: 'Last run at: `r Sys.time()`'
output:
  html_document
bibliography: ~/bibliography.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(knitr)
```

# Purpose

To test:

 * [auto-inclusion](http://rmarkdown.rstudio.com/html_document_format.html#shared_options) of the `_output.yaml` file;
 * [tabsets](http://rmarkdown.rstudio.com/html_document_format.html#tabbed_sections)

Key packages used:

 * base R - for the basics [@baseR]
 * knitr - to create this document [@knitr]
 
# Auto-yaml

Anything below (within) the `output:` container seems to be OK in the yaml file. But not title, author etc. nor the bibliograpphy option. Which is a bit of a pain...

# Tabset Heading {.tabset}

This is really very useful...

## mtcars

```{r }
kable(caption = "mtcars",
      summary(mtcars)
)
```

## ChickWeight

```{r }
kable(caption = "ChickWeight",
      summary(ChickWeight)
)
```


## PlantGrowth

```{r }
kable(caption = "PlantGrowth",
      summary(PlantGrowth)
)
```


# References